---
title: "The Relationship Between Self-esteem and Music Preference"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: flatly
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(tidyverse)
library(plotly)
library(DT)
library(ggcorrplot)
library(ggthemes)

theme_set(theme_igray())

data_df <- read.csv('data.csv')

```

Spotify results
======================================================

Abstract {.sidebar}
-------------------------------------------------------

People who suffer from mental health issues, such as depression, tend to have low self-esteem based on previous studies. Studies have found that music and music-therapy improve self-esteem. However, all of these experiments have been conducted in a controlled environment and none in the context of everyday music. Most people experience variations in self-esteem in the cause of their life, especially during their teenage years. Therefore, it would be useful if the finding that music-therapy improves self-esteem is extended to include everyday music.

In this study, we measured if there was a correlation between self-esteem and everyday music. The purpose of this study is to present a systematic review of the data we have collected concerning our clinical question. We have conducted our experiment utilizing an online questionnaire, using the Gold MSI musical sophistication test and the Rosenberg self-esteem questionnaire. Additionally, the participants were asked to give their “Top Songs 2019” playlist on Spotify. We have found that there is a positive relationship between self-esteem and uplifting music.

```{r}

```

Big visualization{.tabset}
--------------------------------------------------------

### Spotify features
```{r}

fig <- ggplotly( data_df %>% select(valence, energy, mode, dance, rse_score, msi_score) %>% pivot_longer(c(valence, energy, mode, dance), names_to = 'spotify', values_to = 'value') 
          %>% ggplot(aes(x = rse_score, y = value, color = msi_score)) 
          + geom_point() 
          + scale_color_gradient(name = "MSI-scores", 
                        low = "blue", high = "red") 
          + geom_smooth() 
          + facet_wrap(~ spotify) 
          + xlim(c(0,30)) 
          + ylim(c(0,1)) 
          + xlab('Spotify score')  
          + ylab('RSE-scores') )
fig

```

<!-- ### Danceability  -->

<!-- ```{r} -->

<!-- dancingscore <- ggplot(data_df, aes(x = data_df$dance, y = data_df$rse_score)) +  -->
<!--   geom_point() + -->
<!--   ggtitle('Correlation with Self-esteem') + -->
<!--   xlim(c(0,1)) + -->
<!--   ylim(c(0,30)) +  -->
<!--   ylab('RSE Score') + -->
<!--   xlab('Danceability') + -->
<!--   theme_classic() -->

<!-- ggplotly(dancingscore) -->

<!-- ``` -->

<!-- ### Energy  -->

<!-- ```{r} -->
<!-- energyscore <- ggplot(data_df, aes(x = data_df$energy, y = data_df$rse_score)) +  -->
<!--   geom_point() + -->
<!--   ggtitle('Correlation with Self-esteem') + -->
<!--   xlim(c(0,1)) + -->
<!--   ylim(c(0,30)) +  -->
<!--   ylab('RSE Score') + -->
<!--   xlab('Energylevel') + -->
<!--   theme_classic() -->

<!-- ggplotly(energyscore) -->

<!-- ``` -->

<!-- ### Valence  -->

<!-- ```{r} -->
<!-- valencescore <- ggplot(data_df, aes(x = data_df$valence, y = data_df$rse_score)) +  -->
<!--   geom_point() + -->
<!--   ggtitle('Correlation with Self-esteem') + -->
<!--   ylab('RSE Score') + -->
<!--   xlim(c(0,1)) + -->
<!--   ylim(c(0,30)) +  -->
<!--   xlab('Valence') + -->
<!--   theme_classic() -->

<!-- ggplotly(valencescore) -->

<!-- ``` -->

<!-- ### Mode  -->

<!-- ```{r} -->
<!-- modescore <- ggplot(data_df, aes(x = data_df$mode, y = data_df$rse_score)) +  -->
<!--   geom_point() + -->
<!--   ggtitle('Correlation with Self-esteem') + -->
<!--   xlim(c(0,1)) + -->
<!--   ylim(c(0,30)) +  -->
<!--   ylab('RSE Score') + -->
<!--   xlab('Mode') + -->
<!--   theme_classic() -->

<!-- ggplotly(modescore) -->

<!-- ``` -->

### All correlations

```{r}
dataslice = select(data_df, -X, -results.education, -demographics.gender, -demographics.occupation)
corr <- round(cor(dataslice), 1)
p.mat <- cor_pmat(dataslice)
corrplotspotify <- ggcorrplot(corr, hc.order = TRUE,
    type = "lower", p.mat = p.mat)
corrplotspotify
```

Background 
========================================================

Column {data-width=250}
-----------------------------------------------------------------------

### Hypotheses

```{r}

```

There is a positive relationship between self-esteem and uplifting music. 

### Statistical findings

```{r}

```

Column {data-width=400 .tabset}
-----------------------------------------------------------------------

### Theory

Most people seem to have experienced how our music and self-esteem go hand in hand. However, the relation between the two may differ per person, making the research of music and self-esteem an interesting topic. With this research, we want to find out the influences of music and self-esteem on each other.

Previous studies have shown that music therapy improves self-esteem in people. An example of such a study is the scientific article Use of Music Therapy for Enhancing Self-esteem among Academically Stressed Adolescents  written by Mamta Sharma and Tanmeet Jagdev from Punjabi University.

The experiment conducted in this study consisted of 30 students who have high academic stress and low self-esteem split into two groups. One group was selected for music therapy while the other group was the control group. The participants’ stress level and self-esteem was measured using the Scale of Academic Stress and the Self Esteem Inventory. The experimental group was instructed to listen and enjoy a 30-minute flute recording of raga, a melodic mode used in Indian classical music, daily for 15 days. Results show that the experimental group had a higher self-esteem than the control group. The difference between the two groups was statistically significant, proving that music therapy improves self-esteem.

In the article Music listening as self-enhancement: Effects of empowering music on momentary explicit and implicit self-esteem by Paul Elvers, Timo Fischger and Jochen Steffens, they make a distinction between momentary explicit self-esteem and implicit self-esteem. In both cases, they seem to be affected by music listening but in different ways. Explicit self-esteem changed positively because of liking while implicit self-esteem changed positively because of empathy and negatively because of nostalgia.

Interestingly, all these experiments have been done in a controlled environment, in which the experimenters told the participants to listen to specific songs, but none have studied self-esteem in the context of everyday music listening, in which we have control over what we listen to. With this research, we want to see whether everyday music can cause similar effects as music therapy. If that is the case, then this may be an accessible solution to help those suffering from low self-esteem. As there is currently no research regarding this particular topic, our research as an exploratory one that could potentially form a basis for future research into everyday music and self-esteem.


```{r}

```

### Methods

```{r}

```

**Participants**

The participants were 55 Spotify-users who filled in the “Does music define your self?” questionnaire. An additional 15 people filled in the questionnaire but were excluded from the final sample because of not submitting a link to a Spotify “Your Top Songs 2019” playlist. The sample was composed of 21 females and 21 males with a mean age of 21 years, ranging between 15 and 31. Most participants are currently in university. The highest educational level the participants finished varied.

**Procedures**

The online questionnaire “Does music define your self?” was shared via social media. Those who got the link to the questionnaire and decided to fill it in, had to follow instructions and answer a series of questions shown on their screens. First, the participants had to paste the link to their “Your Top Songs 2019” Spotify playlist, as their most listened to songs may reveal something about their self-esteem. They proceeded by answering social demographic questions regarding their gender, age, occupational status and highest achieved educational level. Next, they answered the Gold MSI sophistication test and finally the Rosenberg self-esteem questionnaire.
Aach participant got a musical sophistication index and a self-esteem score, based on their results of the Gold MSI musical sophistication test and the Rosenberg self-esteem questionnaire. Using the Spotify API, we found the values of the audio features of each song in their playlist and calculated the average values for each feature per participant. Finally, we correlated these values and the musical sophistication index to the person’s self-esteem score.


Column {data-width=350}
---------------------------------------------------------

<!-- ### Demographics -->

<!-- ```{r} -->

<!-- genderplot <- ggplot(data = data_df, aes(x = data_df$demographics.age, y = data_df$rse_score, col = data_df$demographics.gender)) + geom_point() + geom_smooth() + xlab('Age') + ylab('RSE Score') + ggtitle('RSE scores per gender') + theme(legend.title = element_blank()) -->

<!-- ggplotly(genderplot) -->

<!-- ``` -->

### MSI correlated with Self-esteem

```{r}
msiscore <- ggplot(data_df, aes(x = rse_score, y = msi_score, col = demographics.gender)) + 
  geom_point() +
  geom_smooth(aes(group = 1)) +
  labs(color = 'Gender') +
  xlim(c(0,30)) +
  ylim(c(20,100)) + 
  ylab('MSI score ') +
  xlab('RSE score')
  
ggplotly(msiscore)

```

### Number of participants
```{r}

valueBox(count(data_df), icon = 'fa-pencil')

```


<!-- Background{data-navmenu="Details"} -->
<!-- ======================================================== -->

<!-- Column {.tabset} -->
<!-- ----------------------------------------------------------------------- -->



<!-- ### Relevant Article Review 1 -->

<!-- ```{r} -->

<!-- ``` -->

<!-- Column {data-width=350} -->
<!-- ----------------------------------------------------------------------- -->




<!-- Column {data-width=350} -->
<!-- ----------------------------------------------------------------------- -->


Discussion
=========================================================

Column {data-width=350}
-----------------------------------------------------------------------

### Conclusion

```{r}

```

Column {data-width=350}
-----------------------------------------------------------------------

### Limitations

```{r}

```

### Future Research

```{r}

```

Column {data-width=300 .tabset}
------------------------------------------------------------

### Clickable bibliography

Elvers, P., Fischinger, T., & Steffens, J. (2018). Music listening as self-enhancement: Effects of empowering music on momentary explicit and implicit self-esteem. Psychology of Music, 46(3), 307-325

Sharma, M., & Jagdev, T. (2011). Use of music therapy for enhancing self-esteem among academically stressed adolescents. Pakistan Journal of Psychological Research, 27(1), pp-53


### Article review 1

Some useful article review

