---
title: "The Relationship Between Self-esteem and Music Preference"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: flatly
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(DT)

data_df <- read.csv('data.csv')

```

Main results
======================================================

Abstract {.sidebar}
-------------------------------------------------------

```{r}

```

Big visualization{.tabset}
--------------------------------------------------------

### Danceability 

```{r}

dancingscore <- ggplot(data_df, aes(x = data_df$dance, y = data_df$rse_score)) + 
  geom_point() +
  ggtitle('Correlation with Self-esteem') +
  xlim(c(0,1)) +
  ylim(c(0,30)) + 
  ylab('RSE Score') +
  xlab('Danceability') +
  theme_classic()
  
ggplotly(dancingscore)

```

### Energy 

```{r}
energyscore <- ggplot(data_df, aes(x = data_df$energy, y = data_df$rse_score)) + 
  geom_point() +
  ggtitle('Correlation with Self-esteem') +
  xlim(c(0,1)) +
  ylim(c(0,30)) + 
  ylab('RSE Score') +
  xlab('Energylevel') +
  theme_classic()
  
ggplotly(energyscore)

```

### Valence 

```{r}
valencescore <- ggplot(data_df, aes(x = data_df$valence, y = data_df$rse_score)) + 
  geom_point() +
  ggtitle('Correlation with Self-esteem') +
  ylab('RSE Score') +
  xlim(c(0,1)) +
  ylim(c(0,30)) + 
  xlab('Valence') +
  theme_classic()
  
ggplotly(valencescore)

```

### Mode 

```{r}
modescore <- ggplot(data_df, aes(x = data_df$mode, y = data_df$rse_score)) + 
  geom_point() +
  ggtitle('Correlation with Self-esteem') +
  xlim(c(0,1)) +
  ylim(c(0,30)) + 
  ylab('RSE Score') +
  xlab('Mode') +
  theme_classic()
  
ggplotly(modescore)

```

Column
-------------------------------------------------------

### Correlation graph?

```{r}

```

### Something
```{r}



```

Additional Findings 
========================================================

Column {.tabset}
---------------------------------------------------------

### Demographics

```{r}


```

### Musical sophistication correlated with Self-esteem

```{r}
msiscore <- ggplot(data_df, aes(x = data_df$msi_score, y = data_df$rse_score)) + 
  geom_point() +
  ggtitle('Correlation with Self-esteem') +
  xlim(c(20,100)) +
  ylim(c(0,30)) + 
  ylab('RSE score') +
  xlab('MSI score') +
  theme_classic()
  
ggplotly(msiscore)

```

Column {data-width=350}
-----------------------------------------------------------------------

### Information

```{r}

```

Background{data-navmenu="Details"}
========================================================

Column {.tabset}
-----------------------------------------------------------------------

### Theory

```{r}

```

### Relevant Article Review 1

```{r}

```

Column {data-width=300}
-----------------------------------------------------------------------

### Hypotheses

```{r}

```

### Methodology

```{r}

```

Column {data-width=400}
-----------------------------------------------------------------------

### Statistical Findings

```{r}

```

Discussion{data-navmenu="Details"}
=========================================================

Column
-----------------------------------------------------------------------

### Conclusion

```{r}

```

Column {data-width=400}
-----------------------------------------------------------------------

### Limitations

```{r}

```

### Future Research

```{r}

```

Bibliography {data-navmenu="Details"}
=======================================================================

### Clickable list of references

```{r}

``` 

