---
title: "The Relationship Between Self-esteem and Music Preference"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: flatly
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(DT)

data_df <- read.csv('data.csv')

```

Main results
======================================================

Abstract {.sidebar}
-------------------------------------------------------

People who suffer from mental health issues, such as depression, tend to have low self-esteem based on previous studies. Studies have found that music and music-therapy improve self-esteem. However, all of these experiments have been conducted in a controlled environment and none in the context of everyday music. Most people experience variations in self-esteem in the cause of their life, especially during their teenage years. Therefore, it would be useful if the finding that music-therapy improves self-esteem is extended to include everyday music.

In this study, we measured if there was a correlation between self-esteem and everyday music. The purpose of this study is to present a systematic review of the data we have collected concerning our clinical question. We have conducted our experiment utilizing an online questionnaire, using the Gold MSI musical sophistication test and the Rosenberg self-esteem questionnaire. Additionally, the participants were asked to give their “Top Songs 2019” playlist on Spotify. We have found that there is a positive relationship between self-esteem and uplifting music.

```{r}

```

Big visualization{.tabset}
--------------------------------------------------------

### Danceability 

```{r}

dancingscore <- ggplot(data_df, aes(x = data_df$dance, y = data_df$rse_score)) + 
  geom_point() +
  ggtitle('Correlation with Self-esteem') +
  xlim(c(0,1)) +
  ylim(c(0,30)) + 
  ylab('RSE Score') +
  xlab('Danceability') +
  theme_classic()
  
ggplotly(dancingscore)

```

### Energy 

```{r}
energyscore <- ggplot(data_df, aes(x = data_df$energy, y = data_df$rse_score)) + 
  geom_point() +
  ggtitle('Correlation with Self-esteem') +
  xlim(c(0,1)) +
  ylim(c(0,30)) + 
  ylab('RSE Score') +
  xlab('Energylevel') +
  theme_classic()
  
ggplotly(energyscore)

```

### Valence 

```{r}
valencescore <- ggplot(data_df, aes(x = data_df$valence, y = data_df$rse_score)) + 
  geom_point() +
  ggtitle('Correlation with Self-esteem') +
  ylab('RSE Score') +
  xlim(c(0,1)) +
  ylim(c(0,30)) + 
  xlab('Valence') +
  theme_classic()
  
ggplotly(valencescore)

```

### Mode 

```{r}
modescore <- ggplot(data_df, aes(x = data_df$mode, y = data_df$rse_score)) + 
  geom_point() +
  ggtitle('Correlation with Self-esteem') +
  xlim(c(0,1)) +
  ylim(c(0,30)) + 
  ylab('RSE Score') +
  xlab('Mode') +
  theme_classic()
  
ggplotly(modescore)

```

Column {data-width = 250}
-------------------------------------------------------

### Correlation graph?

```{r}

```

### Number of participants
```{r}

valueBox(count(data_df), icon = 'fa-pencil')

```

Additional Findings 
========================================================

Column {.tabset}
---------------------------------------------------------

### Demographics

```{r}

histo <- ggplot(data = data_df, aes(x = data_df$rse_score, fill = data_df$demographics.gender)) + geom_histogram(binwidth = 1) + theme_classic() + xlab('RSE Score') + ggtitle('Histogram RSE scores') + theme(legend.title = element_blank())
  
ggplotly(histo)

```

### Musical sophistication correlated with Self-esteem

```{r}
msiscore <- ggplot(data_df, aes(x = data_df$msi_score, y = data_df$rse_score)) + 
  geom_point() +
  ggtitle('Correlation with Self-esteem') +
  xlim(c(20,100)) +
  ylim(c(0,30)) + 
  ylab('RSE score') +
  xlab('MSI score') +
  theme_classic()
  
ggplotly(msiscore)

```

Column {data-width=350}
-----------------------------------------------------------------------

### Information

```{r}

```

Background{data-navmenu="Details"}
========================================================

Column {.tabset}
-----------------------------------------------------------------------

### Theory

```{r}

```

### Relevant Article Review 1

```{r}

```

Column {data-width=350}
-----------------------------------------------------------------------

### Hypotheses

```{r}

```

### Statistical findings

```{r}

```


Column {data-width=350}
-----------------------------------------------------------------------

### Methods

```{r}

```

Participants:
The participants were 42 Spotify-users who filled in the “Does music define your self?” questionnaire. An additional 11 people filled in the questionnaire but were excluded from the final sample because of not submitting a link to a Spotify “Your Top Songs 2019” playlist. The sample was composed of 20 females and 19 males with a mean age of 25 years, ranging between 15 and 31. Most participants are currently in university. The highest educational level the participants finished varied.

Procedures:
The online questionnaire “Does music define your self?” was shared via social media. Those who got the link to the questionnaire and decided to fill it in, had to follow instructions and answer a series of questions shown on their screens. First, the participants had to paste the link to their “Your Top Songs 2019” Spotify playlist, as their most listened to songs may reveal something about their self-esteem. They proceeded by answering social demographic questions regarding their gender, age, occupational status and highest achieved educational level. Next, they answered the Gold MSI sophistication test and finally the Rosenberg self-esteem questionnaire.
Aach participant got a musical sophistication index and a self-esteem score, based on their results of the Gold MSI musical sophistication test and the Rosenberg self-esteem questionnaire. Using the Spotify API, we found the values of the audio features of each song in their playlist and calculated the average values for each feature per participant. Finally, we correlated these values and the musical sophistication index to the person’s self-esteem score.

Discussion{data-navmenu="Details"}
=========================================================

Column
-----------------------------------------------------------------------

### Conclusion

```{r}

```

Column {data-width=400}
-----------------------------------------------------------------------

### Limitations

```{r}

```

### Future Research

```{r}

```

Bibliography {data-navmenu="Details"}
=======================================================================

### Clickable list of references

```{r}

``` 

